An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-03 poly-embed-journal/poly-embed-journal.tex
Revisiting proof of prop 7 and 4

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant by assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a \jessie{non-redundant} finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{restatable}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	2 $\Rightarrow$ 3: 
	Suppose $\trim(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}

	1 $\Rightarrow$ 4:
%	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
%	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
%	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
%	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
	Since $\Gamma$ embeds a finite property $\gamma$, we have a finite minimum representative set $\Sc$ for $\gamma$ such that $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
	Moreover, $\Theta$ is finite since $\Sc$ is finite.
	It is just left to show each $\theta \in \Theta$ is full-dimensional.
	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
	Since level sets of elicitable properties are closed, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.

@@

	4 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).

@@

>>>>

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a \jessie{non-redundant} finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}
\end{restatable}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	2 $\Rightarrow$ 3: 
	Suppose $\trim(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.
	\jessie{Using the old definition of $\trim$, mirroring ish previous proofs: $\trim(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u $s.t.$ \Gamma_u \subseteq \Gamma_{u'}\}$.
	Take $\U' = \{u_1, \ldots, u_k\}$ to be the finite set of reports forming $\trim$.
	Since $\cup \trim(\Gamma) = \cup_{u \in \U'} = \simplex$, we have $\U'$ representative.
	If $\U'$ is not minimum, there is some $\U \subseteq \U'$ that is minimum with $\card(\U) \leq \card(\U') = k$, which is finite.}

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma|_\U(p) := \Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.
	\jessiet{Want more details here.  It's the forward implication of Prop 4, but since this is used in the reverse implication of prop 4, don't want to create cyclic dependencies.}

	1 $\Rightarrow$ 4:
%	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
%	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
%	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
%	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
	Since $\Gamma$ embeds a finite property $\gamma$, there is an embedding $\varphi$ and a finite minimum representative set $\Sc$ for $\gamma$ such that $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
	(Embedding implies $\Sc$ is a minimum representative set for $\gamma$ iff $\varphi(\Sc)$ is minimum representative for $\Gamma$.)
	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
	Moreover, $\Theta$ is finite since $\Sc$ is finite.
	It is just left to show each $\theta \in \Theta$ is full-dimensional.
	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
	Since level sets of elicitable properties are closed\footnote{$\gamma_r = \Gamma_{\varphi(r)}$ for all $r \in \Sc$, we can use this characteristic about level sets of elicitable properties. \jessie{Adding this since we haven't shown $\gamma$ elicitable yet.}}, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.

@@

	4 $\Rightarrow$ 1: 
	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).

@@

This also prompts us to think about redundancy in properties.
\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}
